---
title: "ESM 244 - Assignment 2, Task 2"
author: "Claire Madden"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

Citation: Columbia River DART, Columbia Basin Research, University of Washington. (2019). Adult Passage Graphics & Text. Available from http://www.cbr.washington.edu/dart/query/adult_graph_text

1.	A useful descriptive introductory summary (3 - 4 sentences) of what’s contained in the project
2.	Image(s), with captions and necessary citation(s), of Bonneville Dam and/or steelhead (or whatever time series data you choose to explore)
3.	All of your organized and well-annotated code (with warnings/messages hidden) used to create at least:

-	A finalized time series plot of the original observations (daily data)
-	A finalized seasonplot to explore if/how monthly passage has shifted over time (I totaled counts by month before doing this...you can choose if you want to do that)
-	A finalized visualization of annual steelhead passage counts 

4.	Make sure that your figures appear in your final knitted document, each with a useful caption. Include text associated with each to help the audience understand and interpret the results. 

```{r}

library(tidyverse)
library(tsibble)
library(fable)
library(fabletools)
library(feasts)
library(forecast)
library(janitor)
library(lubridate)
library(paletteer)

fish_data <- read_csv("cbr_fish_passage_bonneville_allyrs_steelhead.csv") %>% 
  clean_names()

# data explorations

View(fish_data)
unique(fish_data$parameter) # only Stlhd contained in the dataset
unique(fish_data$datatype) # only Adult Passage recorded
class(fish_data$mm_dd) #character format 


```


```{r}
fish_clean <- fish_data %>% 
  mutate(date = paste(mm_dd, year)) %>% # combine date info into a single column
  mutate(ts_date = lubridate::parse_date_time(date, "dmy")) %>% # turn into a recognizable format 
  mutate(ts_date = as.Date(ts_date)) %>% # change class to date
  mutate(month_sep = yearmonth(ts_date)) %>% #not sure if i need this step but leaving it in case
  drop_na(month_sep) %>% # remove na values from month_sep (all are on February 29th which must be considered a 'nonsensical' date in tsibbles brain..?)
  drop_na(value) # drop na observations in value column

# create another dataframe with parsed date data for use later
fish_parse <- fish_clean %>% 
  mutate(new_date = ts_date) %>% # duplicate date column
  separate(new_date, into = c("year", "month", "day"), sep = "-") %>% #seperate date components
  mutate(year = as.numeric(year), # make all date components recognized as numeric (not character)
         month = as.numeric(month),
         day = as.numeric(day))
  
```



```{r}
# timeseries plot of original observations (daily data)
fish_ts_daily <- ggplot(data = fish_clean, aes(x = ts_date, y = value))+
  geom_line()+
  theme_minimal()+
  labs(x = "Date",
       y = "Count of Adult Steelhead Trout \nPassing Bonneville Dam")+
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,35000))

fish_ts_daily

# check out observations since 2000 to see more detail

fish_since2000 <- fish_clean %>% 
  filter(year>=2000)

fish_ts_2000 <- ggplot(data = fish_since2000, aes(x = ts_date, y = value))+
  geom_line()+
  theme_minimal()+
  labs(x = "Date",
       y = "Count of Adult Steelhead Trout \nPassing Bonneville Dam")+
  scale_y_continuous(expand = c(0,0),
                     limits = c(0,35000))

fish_ts_2000 # this one is a lot better for seeing seasonality/yearly peaks
```


```{r}

fish_ts_month <- ggplot(data = fish_clean, aes(x = month_sep, y = value))+
  geom_line()+
  theme_minimal()

fish_ts_month # this one looks the same as daily... 

# seasonplot is not going great ... 

fish_ts <- as_tsibble(fish_clean, index = ts_date) %>% 
  tsibble::fill_gaps() # add this step to make gg_subseries happy

fish_ts %>% autoplot(value)


# need to make a monthly summary of values to make a season plot

fish_month <- fish_clean %>% 
  group_by(month_sep) %>% 
  summarize(month_agg = sum(value)) %>% 
  mutate(year_month = tsibble::yearmonth(month_sep),
         month = month(year_month, label = TRUE),
         year = year(year_month))

fish_month_ts <- as_tsibble(fish_month, index = year_month) %>% 
  tsibble::fill_gaps()

fish_month_ts %>% gg_season(month_agg) # gg_season still not working


month_season_plot <- ggplot(data = fish_month, aes(x = month, y = month_agg, group = year)) +
  geom_line(aes(color = year))+
  


# make season plot with ggplot, which this is not..
#season_plot <- ggplot(data = fish_parse, aes(x = month , y = value, group = year)) +
#  geom_line(aes(color = year), alpha = 0.5)+
#  theme_minimal()+
 # scale_x_continuous(expand = c(0,0),
#                     breaks = seq(1,12,1),
#                     labels = c("January", "February", "March", 
#                                "April", "May", "June", 
#                                "July", "August", "September", 
#                                "October", "November", "December"))+
#  scale_color_paletteer_c("ggthemes::Orange-Blue Diverging")+
#  labs(x = "Month",
#       y = "Count of Adult Steelhead Trout \nPassing Bonneville Dam",
#       color = "Observation Year")+
#  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#  scale_y_continuous(expand = c(0,0))

#season_plot





```



```{r}
# annual passages

fish_year <- fish_clean %>% 
  group_by(year) %>% 
  summarize(annual_agg = sum(value)) %>% 
  mutate(year = year)


fish_year_ts <- ggplot(data = fish_year, aes(x = year, y = annual_agg)) +
  geom_line(aes(color = year))


fish_year_ts

```










