---
title: "assignment2_task3"
author: "Claire Madden"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```
For Task 3, make a map of land use / land cover and watersheds for the big island of Hawaii, accessed from: 

●	Land use/land cover data: http://geoportal.hawaii.gov/datasets/land-use-land-cover-lulc
●	Watershed data: http://geoportal.hawaii.gov/datasets/watersheds

Familiarize yourself with the data attributes (see link), and download the shapefile data for each. After reading the shapefile data into R, make finalized map(s) in which you: 
●	Clearly and professionally show the different land use / land cover types for all main Hawaiian islands, or for an island or region of your choosing
●	Clearly and professionally show the different watersheds for all main Hawaiian islands, or for an island or region of your choosing

There is flexibility! You can decide: 
●	Do you want your maps to be static or interactive?
●	What areas do you want to focus on? 
●	Do you want to show land use/landcover and watersheds in a single map or in separate maps? 
●	Whatever you decide is great, just make sure that your final outputs are presented in a nice professional HTML that you’d be proud to share with someone so that they can see your awesome spatial code! 



```{r}
library(tidyverse)
library(sf)
library(tmap)
library(mapview)
library(here)
library(dplyr)

watersheds <- read_sf(dsn = here("HI_watersheds"), layer = "Watersheds") %>% 
  st_transform(crs = 4326)

landuse <- read_sf(dsn = here("HI_land_use"), layer = "Land_Use_Land_Cover_LULC") %>% 
  st_transform(crs = 4326) #%>% 
  #case_when(landcover == "Bays and Estuaries" | "Lakes" | "Reservoirs" | "Streams and Canals" ~ "water body", landcover == "0" | "Transitional Area" ~ "unknown"))


hi_map <- ggplot()+
  geom_sf(data = watersheds)

hi_map


kauai <- hi_map + 
  coord_sf(xlim = c(-159, -160), ylim = c(21.5, 22.5), expand = FALSE) +
  geom_sf(data = landuse, aes(fill = landcover))

kauai
  
```






