---
title: "ESM 244 - Assignment 2, Task 3"
author: "Claire Madden"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```
For Task 3, make a map of land use / land cover and watersheds for the big island of Hawaii, accessed from: 

●	Land use/land cover data: http://geoportal.hawaii.gov/datasets/land-use-land-cover-lulc
●	Watershed data: http://geoportal.hawaii.gov/datasets/watersheds

Familiarize yourself with the data attributes (see link), and download the shapefile data for each. After reading the shapefile data into R, make finalized map(s) in which you: 
●	Clearly and professionally show the different land use / land cover types for all main Hawaiian islands, or for an island or region of your choosing
●	Clearly and professionally show the different watersheds for all main Hawaiian islands, or for an island or region of your choosing

There is flexibility! You can decide: 
●	Do you want your maps to be static or interactive?
●	What areas do you want to focus on? 
●	Do you want to show land use/landcover and watersheds in a single map or in separate maps? 
●	Whatever you decide is great, just make sure that your final outputs are presented in a nice professional HTML that you’d be proud to share with someone so that they can see your awesome spatial code! 



```{r}
library(tidyverse)
library(sf)
library(tmap)
library(mapview)
library(here)
library(dplyr)
library(paletteer)

watersheds <- read_sf(dsn = here("HI_watersheds"), layer = "Watersheds") %>% 
  st_transform(crs = 4326)

landuse <- read_sf(dsn = here("HI_land_use"), layer = "Land_Use_Land_Cover_LULC") %>% 
  st_transform(crs = 4326) %>% 
  mutate(landcover_rename = case_when(landcover == "Cropland and Pasture" ~ "Agriculture",
                                      landcover == "Commercial and Services" ~ "Industry", 
                                      landcover == "Residential" ~ "Urban", 
                                      landcover == "Evergreen Forest Land" ~ "Undeveloped", 
                                      landcover == "Other Urban or Built-up Land" ~ "Urban",
                                      landcover == "Mixed Rangeland" ~ "Agriculture",
                                      landcover == "Industrial" ~ "Industry",
                                      landcover == "Streams and Canals" ~ "Water", 
                                      landcover == "Orchards, Groves, Vineyards, Nurseries and Ornamental Horticultural Areas" ~ "Agriculture",
                                      landcover == "Shrub and Brush Rangeland" ~ "Agriculture",
                                      landcover == "Forested Wetland" ~ "Undeveloped",
                                      landcover == "Reservoirs" ~ "Water",
                                      landcover == "Nonforested Wetland" ~ "Undeveloped",
                                      landcover == "Bare Exposed Rock" ~ "Undeveloped",
                                      landcover == "Sandy Areas Other than Beaches" ~ "Undeveloped",
                                      landcover == "Transportation, Communications and Utilities" ~ "Industry",
                                      landcover == "Herbaceous Rangeland" ~ "Agriculture",
                                      landcover == "Beaches" ~ "Undeveloped",
                                      landcover == "Other Agricultural Land" ~ "Agriculture",
                                      landcover == "Lakes" ~ "Water",
                                      landcover == "Strip Mines, Quarries, and Gravel Pits" ~ "Industry",
                                      landcover == "Mixed Barren Land" ~ "Undeveloped",
                                      landcover == "Bays and Estuaries" ~ "Water",
                                      landcover == "Mixed Urban or Built-up Land" ~ "Urban",
                                      landcover == "Transitional Areas" ~ "Unknown",
                                      landcover == "0" ~ "Unknown",
                                      landcover == "Industrial and Commercial Complexes" ~ "Industry",
                                      landcover == "Confined Feeding Operations" ~ "Agriculture"))
  


hi_map <- ggplot()+
  geom_sf(data = watersheds)

hi_map


kauai <- ggplot() + 
  geom_sf(data = landuse, aes(fill = landcover_rename), color = NA) + 
  scale_fill_manual(values = c("peru", "indianred4", "darkolivegreen", "grey65", "plum", "cadetblue4"))+
  geom_sf(data = watersheds, fill = NA, color = "white", size = 0.2)+
  coord_sf(xlim = c(-159.2, -159.8), ylim = c(21.8, 22.3), expand = FALSE)+
  theme_minimal()+
  labs(fill = "Landcover Type")

kauai



```






