---
title: "assignment2_task2"
author: "Claire Madden"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

Citation: Columbia River DART, Columbia Basin Research, University of Washington. (2019). Adult Passage Graphics & Text. Available from http://www.cbr.washington.edu/dart/query/adult_graph_text

1.	A useful descriptive introductory summary (3 - 4 sentences) of what’s contained in the project
2.	Image(s), with captions and necessary citation(s), of Bonneville Dam and/or steelhead (or whatever time series data you choose to explore)
3.	All of your organized and well-annotated code (with warnings/messages hidden) used to create at least:

-	A finalized time series plot of the original observations (daily data)
-	A finalized seasonplot to explore if/how monthly passage has shifted over time (I totaled counts by month before doing this...you can choose if you want to do that)
-	A finalized visualization of annual steelhead passage counts 

4.	Make sure that your figures appear in your final knitted document, each with a useful caption. Include text associated with each to help the audience understand and interpret the results. 

```{r}

library(tidyverse)
library(tsibble)
library(fable)
library(fabletools)
library(feasts)
library(forecast)
library(janitor)
library(lubridate)

fish_data <- read_csv("cbr_fish_passage_bonneville_allyrs_steelhead.csv") %>% 
  clean_names()

# data explorations

View(fish_data)
class(fish_data$mm_dd) #character format 


```


```{r}
fish_clean <- fish_data %>% 
  mutate(new_date = mm_dd) %>% 
  separate(new_date, into = c("day", "month"), sep = "-") %>% 
  mutate(date = paste(day, month, year, sep = "-")) %>% 
  dmy(date)
```




